A free/open-source Kazakh-Tatar machine translation system

### 2013-04-16 paper/paper.tex
work-around for MT Summit's broken bst file
Morphological Transducers (section 4.2): check

Kazakh is primarily spoken in Kazakhstan, where it is the national
language, sharing official status with Russian as the FIXME language.
Large groups of native speakers also exist in China, neigbouring
Central-Eurasian republics, and Mongolia. The total number of speakers is at least 10 million people.

@@

Use of lexc allows for straightforward definition of different word classes and subclasses.  For example, Tatar (but not Bashkir) has two classes of verbs: one which take a harmonised high vowel in the infinitive (the default), and one which take a harmonised low vowel in the infinitive.  This was implemented in lexc with two similar continuation lexica for verbs: one pointing at a lexicon with an A-initial infinitive ending, and another pointing at a lexicon with an I-initial infinitive ending.

@@

\subsection{Bilingual lexicon}
\begin{figure*}[htbp]
\begin{texttt}
    <e><p><l>\textbf{юнәлеш}<s n="n"/></l><r>\textbf{йүнәлеш}<s n="n"/></r></p></e> \\
    <e><p><l>\textbf{борын}<s n="n"/></l><r>\textbf{танау}<s n="n"/></r></p></e> \\
    <e><p><l>\textbf{борын}<s n="n"/></l><r>\textbf{морон}<s n="n"/></r></p></e> \\
    <e><p><l>\textbf{ераклык}<s n="n"/></l><r>\textbf{алы{\qipa ҫ}лы{\qipa ҡ}}<s n="n"/></r></p></e> \\
    <e><p><l>\textbf{ераклык}<s n="n"/></l><r>\textbf{йыра{\qipa ҡ}лы{\qipa ҡ}}<s n="n"/></r></p></e>
\end{texttt}
\caption{Example entries from the bilingual transfer lexicon. Tatar is on the left, and Bashkir on the right}
\label{fig:bidix}
%\vspace{-1em}
\end{figure*}

@@

%\bibliographystyle{lrec2012}
%\bibliography{tt-ba}
\bibliographystyle{mtsxiv}
\bibliography{paper}

>>>>

Kazakh is primarily spoken in Kazakhstan, where it is the national
language, sharing official status with Russian as an official language.
Large groups of native speakers also exist in China, neigbouring
Central-Eurasian republics, and Mongolia. The total number of speakers is at least 10 million people.

@@

Use of lexc allows for straightforward definition of different word classes and subclasses.  For example, Tatar (but not Kazakh) has two classes of verbs: one which takes a harmonised high vowel in the infinitive (the default), and one which take a harmonised low vowel in the infinitive.  This was implemented in lexc with two similar continuation lexica for verbs: one pointing at a lexicon with an A-initial infinitive ending, and another pointing at a lexicon with an I-initial infinitive ending.

@@

\subsection{Bilingual lexicon}
%FIXME: Ilnar, we need some good examples here
\begin{figure*}[htbp]
\begin{texttt}
    <e><p><l>\textbf{юнәлеш}<s n="n"/></l><r>\textbf{йүнәлеш}<s n="n"/></r></p></e> \\
    <e><p><l>\textbf{борын}<s n="n"/></l><r>\textbf{танау}<s n="n"/></r></p></e> \\
    <e><p><l>\textbf{борын}<s n="n"/></l><r>\textbf{морон}<s n="n"/></r></p></e> \\
    <e><p><l>\textbf{ераклык}<s n="n"/></l><r>\textbf{алы{\qipa ҫ}лы{\qipa ҡ}}<s n="n"/></r></p></e> \\
    <e><p><l>\textbf{ераклык}<s n="n"/></l><r>\textbf{йыра{\qipa ҡ}лы{\qipa ҡ}}<s n="n"/></r></p></e>
\end{texttt}
\caption{Example entries from the bilingual transfer lexicon. Tatar is on the left, and Bashkir on the right}
\label{fig:bidix}
%\vspace{-1em}
\end{figure*}

@@

%\bibliographystyle{lrec2012}
%\bibliography{tt-ba}
\bibliographystyle{mtsxiv}
%\bibliographystyle{apa}
\bibliography{paper}
